The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-12-02 manuscript/manuscript.qmd
Rearrange theoretical framework figure

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].

Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province. In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020]. For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service. Having the potential to shift programs to other provinces as needed thus provides a form of operational space.

# Theoretical background

@@

## The "closing space" phenomenon - Institutional approach to closing space

@@

```{r fig-theory, fig.width=6, fig.height=2}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational space: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
theory_nodes <- tribble(
  ~id, ~name, ~x, ~y, ~highlight,
  1,   "Issue contentiousness", 1, 0, FALSE,
  2,   "Operational space", 3, 0, TRUE,
  3,   "Local focus", 2, 1, FALSE,
  4,   "Government preferences", 2, -1, FALSE
)

@@

ggraph(theory_graph, x = x, y = y) + 
  geom_edge_link(
    aes(
      start_cap = label_rect(node1.name, padding = margin(10, 5, 10, 5, "pt")),
      end_cap = label_rect(node2.name, padding = margin(10, 5, 10, 5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  geom_node_label(
    aes(x = x, y = y, label = name, fill = highlight), 
    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
  ) +
  scale_x_continuous(expand = expansion(add = 0.3)) +
  scale_y_continuous(expand = expansion(add = 0.2)) +
  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
  )
```

>>>>

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.

# Closing space, differential enforcement, and INGO operational space

The 2017 ONGO Law's provision of two legal pathways for registration is an example of administrative crackdown [@Chaudhry:2022] an example of fit within the broader global phen

Why crack down?

To situate our analysis of the impacts of China's ONGO Law in existing work on closing civic space, we propose a theoretical framework to explain

---

The government can thus use the RO registration process to limit the potential reach of INGOs.

In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020]. For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service. Having the potential to shift programs to other provinces as needed thus provides a form of operational space.

@@

@@

```{r fig-theory, fig.width=6, fig.height=1.75}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational space: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
theory_nodes <- tribble(
  ~id, ~name, ~x, ~y, ~highlight,
  1,   "Issue contentiousness", 2, 1, FALSE,
  2,   "Operational space", 2, 0, TRUE,
  3,   "Local focus", 3, 1, FALSE,
  4,   "Government preferences", 1, 1, FALSE
)

@@

ggraph(theory_graph, x = x, y = y) + 
  geom_edge_link(
    aes(
      start_cap = label_rect(node1.name, padding = margin(10, 0, 10, -05, "pt")),
      end_cap = label_rect(node2.name, padding = margin(10, -5, 10, -5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  geom_node_label(
    aes(x = x, y = y, label = name, fill = highlight), 
    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
  ) +
  scale_x_continuous(expand = expansion(add = 0.4)) +
  scale_y_continuous(expand = expansion(add = 0.2)) +
  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
  )
```
